Finch: Sparse and Structured Array Programming with Control Flow

### 2024-03-27 main.tex
Update on Overleaf.
move figures
fix

% Language setting
% Replace `english' with e.g. `spanish' to change the document language
\usepackage[english]{babel}
\usepackage{subcaption}
% Useful packages
\usepackage{amsmath}
\usepackage{graphicx}
%\usepackage{amssymb}
\usepackage{mathtools}
\usepackage{array}
\usepackage{minted}
\usepackage{ifthen}
\usepackage{ebproof}
\ebproofset{label separation=0pt}
\usepackage{multirow}
%

@@

>>>>

% Language setting
% Replace `english' with e.g. `spanish' to change the document language
\usepackage[english]{babel}
\usepackage{subcaption}
% Useful packages
\usepackage{amsmath}
\usepackage{graphicx}
\graphicspath{{figures/}}
%\usepackage{amssymb}
\usepackage{mathtools}
\usepackage{array}
\usepackage{minted}
\usepackage{ifthen}
\usepackage{ebproof}
\ebproofset{label separation=0pt}
\usepackage{multirow}
\usepackage{wrapfig}

\makeatletter
\DeclareFontFamily{OMX}{MnSymbolE}{}
\DeclareSymbolFont{MnLargeSymbols}{OMX}{MnSymbolE}{m}{n}
\SetSymbolFont{MnLargeSymbols}{bold}{OMX}{MnSymbolE}{b}{n}
\DeclareFontShape{OMX}{MnSymbolE}{m}{n}{
    <-6>  MnSymbolE5
   <6-7>  MnSymbolE6
   <7-8>  MnSymbolE7
   <8-9>  MnSymbolE8
   <9-10> MnSymbolE9
  <10-12> MnSymbolE10
  <12->   MnSymbolE12
}{}
\DeclareFontShape{OMX}{MnSymbolE}{b}{n}{
    <-6>  MnSymbolE-Bold5
   <6-7>  MnSymbolE-Bold6
   <7-8>  MnSymbolE-Bold7
   <8-9>  MnSymbolE-Bold8
   <9-10> MnSymbolE-Bold9
  <10-12> MnSymbolE-Bold10
  <12->   MnSymbolE-Bold12
}{}

\let\llangle\@undefined
\let\rrangle\@undefined
\DeclareMathDelimiter{\llangle}{\mathopen}%
                     {MnLargeSymbols}{'164}{MnLargeSymbols}{'164}
\DeclareMathDelimiter{\rrangle}{\mathclose}%
                     {MnLargeSymbols}{'171}{MnLargeSymbols}{'171}
\makeatother

@@

\newcommand{\rothead}[1]{\rotatebox{90}{\textbf{#1}}}
